---
title: "Work with files from a Google Drive folder"
date: '`r format(Sys.time(), "%A %B %d %Y %X %Z")`'
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
options(
  gargle_oauth_cache = ".secrets",
  gargle_oauth_email = "eli.holmes@noaa.gov"
)
googledrive::drive_deauth()
googledrive::drive_auth(scopes = "https://www.googleapis.com/auth/drive.readonly", email="eli.holmes@noaa.gov")
url_googledrive <- "https://drive.google.com/drive/folders/11WnXxs56jORbLkD1mFTZxwSaShex3Sse"
id_googledrive <- "11WnXxs56jORbLkD1mFTZxwSaShex3Sse"
```

# Download files

## List files in a google drive folder

All files.
```{r}
dir_files <- googledrive::drive_ls(path = url_googledrive)
dir_files$name
```

All csv files.
```{r}
dir_files <- googledrive::drive_ls(path = url_googledrive, type="csv")
dir_files$name
```

All Excel files.
```{r}
dir_files <- googledrive::drive_ls(path = url_googledrive, type="xlsx")
dir_files$name
```

All Google Spreadsheets.
```{r}
dir_files <- googledrive::drive_ls(path = url_googledrive, type="spreadsheet")
dir_files$name
```

All Google Documents.
```{r}
dir_files <- googledrive::drive_ls(path = url_googledrive, type="document")
dir_files$name
```

## Download a file

First get the files in the folder.
```{r}
a <- googledrive::drive_ls(path = url_googledrive)
```

### Download one Excel file

Download from Google Drive and save to a folder called `data`.

```{r}
file_name <- "data.xlsx"
# find the id of that file
file_id <- a$id[which(a$name==file_name)]
# download the file and save to data folder
googledrive::drive_download(file=file_id, overwrite = TRUE, path = file.path("data", file_name))
```

Read that file in using the **readxl** package.
```{r}
tmp <- readxl::read_excel(file.path(here::here(), "data", "data.xlsx"))
tmp
```

## Download one csv file

Download from Google Drive and save to a folder called `data`.

```{r}
file_name <- "Stone.csv"
file_id <- a$id[which(a$name==file_name)]
googledrive::drive_download(file=file_id, overwrite = TRUE, path = file.path("data", file_name))
```

Read that file in. The first 2 lines are metadata and are skipped.
```{r}
tmp <- read.csv(file.path(here::here(), "data", file_name), skip=2)
tmp
```

### Download csv files

Download all csv files and save to a folder called `data`.

```{r}
a <- googledrive::drive_ls(path = url_googledrive, type = "csv")
for (i in 1:nrow(a)){
  googledrive::drive_download(a$id[i], overwrite = TRUE, path = file.path("data", a$name[i]))
}
```

### Download Google Spreadsheets

```{r}
a <- googledrive::drive_ls(path = url_googledrive, type = "spreadsheet")
for (i in 1:nrow(a)){
  googledrive::drive_download(a$id[i], type = "csv", overwrite = TRUE, path = file.path("data", a$name[i]))
}
```

## Pushing results up to GitHub

Here I show how you might use the [**gert**](https://CRAN.R-project.org/package=gert) package. Note this works because I am doing it within RStudio and my RStudio set-up has permission to push to this repo. If you don't have RStudio set-up to push to GitHub, then you need to set that up first. Also you need to be working in the local repo of the GitHub repo that your are pushing to. This sounds more complicated than it is.
```{r eval=FALSE}
gert::git_add(file.path("data", "Stone.csv"))
gert::git_commit("Adding a file", author = "Eli Holmes <eli.holmes@noaa.gov>")
gert::git_push(remote = "origin", repo = ".")
```

You can also use these set ups to set up your code to run from GitHub via GitHub Actions. If the Google Drive is not publicly viewable, then you'll need to research how to set up authorization in a deployed application [read this](https://gargle.r-lib.org/articles/non-interactive-auth.html). But if the Google Drive is publicly viewable, then it is fairly easy to set up a Google Action that is triggered on a schedule or triggered by an outside event. [Read about how to do that here](https://docs.github.com/en/actions/learn-github-actions/events-that-trigger-workflows).
